TBD

### 2016-10-11 paper.tex
need to rewrite stefcal section
started conjugate gradient section

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
\usepackage{subfigure}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{graphicx}

\newcommand{\bz}{\bmath{z}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\bB}{\bmath{B}}
\newcommand{\bC}{\bmath{C}}
\newcommand{\bE}{\bmath{E}}
\newcommand{\bF}{\bmath{F}}
\newcommand{\bG}{\bmath{G}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\bH}{\bmath{H}}
\newcommand{\bN}{\bmath{N}}
\newcommand{\bM}{\bmath{M}}
\newcommand{\bI}{\bmath{I}}
\newcommand{\ba}{\bmath{a}}
\newcommand{\bb}{\bmath{b}}
\newcommand{\bzero}{\bmath{0}}
%\newcommand{\bvarrho}{\bmath{\varrho}}
%\newcommand{\bnu}{\bmath{\nu}}
%\newcommand{\bvarphi}{\bmath{\varphi}}
\newcommand{\conj}[1]{\overline{#1}}

@@

@@

Interestingly enough, if we substitute $\alpha = 1$ into Eq.~\ref{eq:g_update} then it reduces to the skymodel-based StEFCal update rule.

@@

\begin{eqnarray}
\begin{bmatrix} \Delta \boldsymbol{z}\\ \Delta \conj{\boldsymbol{z}} \end{bmatrix} &\approx& \widetilde{\boldsymbol{H}}^{-1}\boldsymbol{J}^H(\breve{\boldsymbol{d}}-\breve{\boldsymbol{v}})\\ 
&=& \widetilde{\boldsymbol{H}}^{-1}\boldsymbol{J}^H\breve{\boldsymbol{d}} -  \widetilde{\boldsymbol{H}}^{-1}\widetilde{\boldsymbol{H}}\breve{\boldsymbol{z}}\\
\breve{\boldsymbol{z}}_{k+1} &\approx& \widetilde{\boldsymbol{H}}^{-1}\boldsymbol{J}^H\breve{\boldsymbol{d}}
\end{eqnarray}

Levenberg-Marquardt:

\begin{eqnarray}
\breve{\boldsymbol{z}}_{k+1} &\approx& \frac{1}{1+\lambda}\widetilde{\boldsymbol{H}}^{-1}\boldsymbol{J}^H\breve{\boldsymbol{d}} + \frac{\lambda}{1+\lambda} \breve{\boldsymbol{z}}_k\\
 &=& \alpha \widetilde{\boldsymbol{H}}^{-1}\boldsymbol{J}^H\breve{\boldsymbol{d}} + (1-\alpha)\breve{\boldsymbol{z}}_k 
\end{eqnarray}

@@

a very fast computational calibration This linearization trick improves

cite the complex paper has proposed to extend the problem into [RW HERE NEED TO STATE BETTER] its conjugate domain and then to solve for the parameters and there complex conjugates. This can be accomplished
if we introduce Wirtinger derivatives. (I have to look into how to write this better).

The solution to Eq. can now be obtained by using a gradient type of minimization algorithm, like GN and LM.

The GN update rule is given by\\

GN UPDATE RULE

>>>>

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
\usepackage{subfigure}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

\newcommand{\bz}{\bmath{z}}
\newcommand{\bA}{\bmath{A}}
\newcommand{\bB}{\bmath{B}}
\newcommand{\bC}{\bmath{C}}
\newcommand{\bE}{\bmath{E}}
\newcommand{\bF}{\bmath{F}}
\newcommand{\bG}{\bmath{G}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\bn}{\bmath{n}}
\newcommand{\by}{\bmath{y}}
\newcommand{\bJ}{\bmath{J}}
\newcommand{\bD}{\bmath{D}}
\newcommand{\bH}{\bmath{H}}
\newcommand{\bN}{\bmath{N}}
\newcommand{\bM}{\bmath{M}}
\newcommand{\bI}{\bmath{I}}
\newcommand{\ba}{\bmath{a}}
\newcommand{\bb}{\bmath{b}}
\newcommand{\bx}{\bmath{x}}
\newcommand{\bp}{\bmath{p}}
\newcommand{\bzero}{\bmath{0}}
%\newcommand{\bvarrho}{\bmath{\varrho}}
%\newcommand{\bnu}{\bmath{\nu}}
%\newcommand{\bvarphi}{\bmath{\varphi}}
\newcommand{\conj}[1]{\overline{#1}}

@@

\section{Conjugate Gradient Method}

The conjugate gradient method is an iterative method which is used to solve large linear systems, i.e.
\begin{equation}
\label{eq:linear_system}
\bb = \bA\bx,
\end{equation}
where $\bb$ is a known complex column vector, $\bx$ is the unknown complex column vector with the same length as $\bb$, and $\bA$ is a square complex matrix with appropriate dimensions.  
The conjugate gradient method can in general only be applied to the above linear system if $\bA$ is a square positive-definite or a positive semi-definite Hermitian matrix. If
$\bA$ is a square positive semi-definite Hermitian matrix, then the conjugate gradient method only converges if $\bb$ is in the column range of $\bA$ (cite Lu2016). Moreover, using the 
conjugate gradient method to solve Eq.~\eqref{eq:linear_system} will only be computationally advantageous if $\bA$ is also sparse (contain many zero entries).

The Conjugate Gradient method was independently discovered by Hestenes and Stiefel. They later published a joint paper, n, which is now considered as the seminal
reference on CG. Kaniel was able to determined convergence bounds for CG using Chebyshev polynomial. A much more in depth analysis of CG convergence was conducted 
by van erSluis and van der Vorst. Reid is credited for popularizing CG as an iterative method that can be used to solve sparse linear systems.

In the early fifties, the method of Conjugate Gradients
was discovered independently by Hestenes [10] and Stiefel [15]; shortly thereafter, they jointly published
what is considered the seminal reference on CG [11]. Convergence bounds for CG in terms of Chebyshev
polynomials were developed by Kaniel [12]. A more thorough analysis of CG convergence is provided by
van der Sluis and van der Vorst [16]. CG was popularized as an iterative method for large, sparse matrices
by Reid [13] in 1971.

\begin{algorithm}
\caption{Conjugate Gradient Method}\label{algo:extrap_algo}
\begin{algorithmic}[1]
\State $\br_0 \gets \bA\bx_0 - \bb$
\State $\bp_0 \gets -\br_0$
\State $\bmath{u} \gets \text{linspace}(u_{\text{min}},u_{\text{max}},u_{\text{dim}})$
\State $\bmath{v} \gets \text{linspace}(v_{\text{min}},v_{\text{max}},v_{\text{dim}})$ 
\State $g_{pq} \gets \text{zeros}((u_{\text{dim}},v_{\text{dim}}),\text{dtype}=\text{complex})$ \Comment {define your 2D extrapolated regular $uv$-grid}
\State $i \gets 1$
\For{$i\leq u_{\text{dim}}$}  
\State $j \gets 1$
\For{$j\leq v_{\text{dim}}$}  
\State $\bb \gets (\bmath{u}_i,\bmath{v}_j)^T$
%\State $\Rcal \gets \left\{ \sum_{k\in\mathcal{K}}A_k e^{-2\pi i [\widehat{X}_{rs} \circ \widehat{X}^{-1}_{pq}(\bb)]^T\cdot\bs_k} \right \}_{rs}$
%\State $\Mcal \gets \left\{ \sum_{h\in\mathcal{H}}A_h e^{-2\pi i [\widehat{X}_{rs} \circ \widehat{X}^{-1}_{pq}(\bb)]^T\cdot\bs_h} \right \}_{rs}$
%\Comment {with $\mathcal{K}$ containing the index values of all the sources in the field of view and $\mathcal{L}$ containing the index values of the sources that are included in the
%calibration model}
%\State $\Gcal \gets \text{calibrate}(\Rcal,\Mcal)$
%\Comment {any calibration algorithm can be used here (we assume here that the algorithm outputs $\Gcal$)}
%\State $g_{pq}^{ij} \gets [\Gcal]_{pq}$
\State $j \gets j + 1$
\EndFor
\State $i \gets i + 1$
\EndFor
\end{algorithmic}
\end{algorithm}

@@

Interestingly enough, if we substitute $\alpha = 1$ into Eq.~\ref{eq:g_update} then it reduces to the skymodel-based StEFCal update rule. In Chengular they propose 
an $\alpha = 0.3$.

@@

****\\

@@
